---
title: "adae"
author: "Krishna Kumar Shrestha"
date: "July 11, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Installing library and importing data




```{r}
library(haven)
library(dplyr)

library(lubridate)

adsl <- read_sas("C:/Users/krishna/Desktop/adam/adsl.sas7bdat", 
    NULL)
adae <- read_sas("C:/Users/krishna/Desktop/adam/adae.sas7bdat", 
    NULL)

ae <- read_sas("C:/Users/krishna/Desktop/sdtm/ae.sas7bdat", 
    NULL)

```



# Variable no 1  and 3

```{r}

adae1<- ae %>% select(STUDYID,USUBJID,AESTDTC)


```


# variable 2 and 4:19

```{r}
dumy1 <- adsl %>% select(SITEID,USUBJID,
LTSUBJID,
AGE,
AGEU,
SEX,
RACE,
COUNTRY,
PPROTFL,
SCRNFL,
SAFFL,
ENRLFL,
ITTEFL,
LTFUFL,
TRT01P,
TRT01PN,
TRT01A,
TRT01AN
)


adae1 <- adae1 %>% full_join(dumy1) %>% na.omit()
rm(dumy1)

```




# variable 20: 23
ADSL.TRT01P
ADSL.TRT01PN
ADSL.TRT01A
ADSL.TRT01AN
TRTP
TRTPN
TRTA
TRTAN


```{r}

dumy1<- adsl %>% select(TRT01P,TRT01PN,TRT01A,TRT01AN,USUBJID) %>%
  rename(TRTP=TRT01P,TRTPN=TRT01PN,TRTA=TRT01A,TRTAN=TRT01AN)

adae1 <- adae1 %>% full_join(dumy1) %>% na.omit()
rm(dumy1)


```



# vaiable no 24 :33



```{r}



a<- adsl %>% select(TRTSDT,
TRTEDT,
MNTEDT,
HISDEP,
HISDEPFL,
HISSUI,
HISSUIFL,
HISANX,
HISANXFL,USUBJID)
adae1 <- adae1 %>% full_join(a) %>% na.omit()
rm(a)

```


# 36 ASTDT


If the start day is missing, the first of the month will be used unless this is before the start date of study treatment; in this case the study treatment start date will be used.


```{r}

a<- adae1
a$AESTDTC <- ymd(a$AESTDTC,truncated = 1)


a <- a %>% mutate(ASTDT=case_when(
  AESTDTC <= TRTSDT~ as.Date(TRTSDT),
  TRUE ~ as.Date(AESTDTC)
))%>%   select(ASTDT,USUBJID)


adae1 <- full_join(adae1,a)
rm(a)

```


#37


DDMONYYYY format of non-missing AE.AESTDTC. If date is partial then replace missing elements with -.
ADAE.ASTDTC



```{r}

a<- adae1
a$AESTDTC <- ymd(a$AESTDTC)
a <- a%>% mutate(ASTDTC=AESTDTC)
a$ASTDTC<-format(a$ASTDTC, "%d/%b/%Y")
a$ASTDTC[is.na(a$ASTDTC)]<-"-"


```





```{r}

df<- adae1
library(tidyr)

df <- df %>% separate(AESTDTC, c("A", "B","C"))

df <- df %>% select(A,B,C)


```




