---
title: "ADSL"
author: "Krishna Kumar Shrestha"
date: "7/1/2020"
output: html_document
---



```{r}

library(tidyr)
library(readxl)
library(dplyr)

library(haven)

dm <- read_sas("sdtm/dm.sas7bdat", 
               NULL)

sc <- read_sas("sdtm/sc.sas7bdat", 
               NULL)
ds <- read_sas("sdtm/ds.sas7bdat", 
               NULL)
suppdv <- read_sas("sdtm/suppdv.sas7bdat", 
                   NULL)

vs <- read_sas("sdtm/vs.sas7bdat", NULL)
adsl <- read_sas("adam/adsl.sas7bdat", NULL)
co <- read_sas("sdtm/co.sas7bdat", NULL)
lb <- read_sas("sdtm/lb.sas7bdat", NULL)

sv <- read_sas("sdtm/sv.sas7bdat", NULL)
suppdm <- read_sas("sdtm/suppdm.sas7bdat", 
    NULL)
ce <- read_sas("sdtm/ce.sas7bdat", NULL)

lb <- read_sas("sdtm/lb.sas7bdat", NULL)
ex <- read_sas("sdtm/ex.sas7bdat", NULL)
suppce <- read_sas("sdtm/suppce.sas7bdat", 
    NULL)

```




# ALL PREDECESSOR


```{r}

adsl_1<- dm %>% select(STUDYID,INVID,INVNAM,SITEID,USUBJID,SUBJID,AGE,AGEU,BRTHDTC,SEX,RACE,ETHNIC,COUNTRY,ARM,ARMCD,ACTARM,ACTARMCD,DTHFL)


```





#10



```{r}
adsl_1 <- adsl_1 %>% mutate(AGEGR1=case_when(
  AGE < 35  ~ "<35",
  AGE>=35 & AGE < 50 ~ "35-50",
  AGE>=50 ~ ">50"
))


```


#11

```{r}


adsl_1<-adsl_1 %>% mutate(AGEGR1N=case_when(
  AGE<35 ~ 1,
  AGE>=35 & AGE<50 ~2,
  AGE>=50~3
))



```

#12
```{r}
adsl_1<- adsl_1 %>% mutate(AGEGR2= case_when(
  AGE<=18 ~ "<18",
  AGE>18 & AGE<=64 ~"19-64",
  AGE>64 ~">=65"
))
```

#13


```{r}
adsl_1 <-  adsl_1 %>% mutate(AGEGR2N=case_when(
  AGE<=18~ 1,
  AGE>=19 & AGE<=64 ~2,
  AGE>64 ~3
))




```

#14
```{r}
adsl_1 <-adsl_1 %>% mutate(AGEGR3=case_when(
  AGE>17 & AGE<=64 ~"18-64",
  AGE>64 & AGE<=84 ~"65-84",
  AGE>=84 ~">=85"
))
```
#15
```{r}
adsl_1 <- adsl_1 %>% mutate(AGEGR3N= case_when(
  AGE>17 & AGE<=64 ~ 1,
  AGE>64 & AGE<=84 ~ 2,
  AGE>=84 ~ 3
))
```


#16
```{r}
adsl_1<- adsl_1 %>% mutate(AGEGR4=case_when(
  AGE<50 ~ "<50",
  AGE>=50 ~ ">=50"
))
```
#17
```{r}
adsl_1<-adsl_1 %>% mutate(AGEGR4N=case_when(
  AGE<50 ~ 1,
  AGE >=50 ~ 2
))
```


#20
```{r}
adsl_1 <- adsl_1 %>% mutate(SEXN= case_when(
  SEX == "M" ~ 2,
  TRUE ~ 1
))
```


#21
SC.SCSTRESC WHERE SC.SCTESTCD = "GENDER"


```{r}
a1 <- sc %>% 
  filter(SCTESTCD == "GENDER") %>% 
    distinct(USUBJID,.keep_all = TRUE) %>% 
  mutate(SRGENDER=SCSTRESC) %>%
  select(USUBJID,SRGENDER,SCSTRESC)

adsl_1<- adsl_1 %>%
  full_join(a1)


  
  
```


#22

Numeric code variable of SRGENDER.



```{r}
adsl_1 <- adsl_1 %>% 
  mutate(SRGENDRN=case_when(
    SRGENDER =="FEMALE"~1,
    TRUE~2
  )
)


```



#24

```{r}
adsl_1 <-adsl_1 %>% mutate(RACEN=case_when(
  RACE == "AMERICAN INDIAN OR ALASKA NATIVE"~1,
RACE =="ASIAN"~2,
RACE=="BLACK OR AFRICAN AMERICAN"~3,
RACE=="MULTIPLE"~4,
RACE=="WHITE"~6
  ))
```





#25


```{r}


L<- suppdm %>% filter(QNAM == "RACEOR") 





```



#27

```{r}
adsl_1 <- adsl_1 %>% mutate(RACEGR1= case_when(
  RACE == "WHITE" ~ "WHITE",
  RACE == NA ~ "MISSING",
  RACE != "WHITE" ~ "NON WHITE"
))

```
#28
```{r}
adsl_1 <- adsl_1 %>% mutate(RACEGR1N=case_when(
  RACEGR1== "WHITE" ~ 1,
  RACEGR1 =="NON WHITE" ~ 2,
  RACEGR1 == NA ~ 3
  ))
```


#29


```{r}

adsl_1 <-adsl_1 %>% mutate(RACEGR2=case_when(
  RACE=="BLACK OR AFRICAN AMERICAN" ~ "BLACK/AFRICAN AMERICAN",
  !is.na(RACE) ~ "NON-BLACK/AFRICAN AMERICAN",
  is.na(RACE)~ "MISSING"
  ))


```



#30

```{r}
adsl_1 <-adsl_1 %>% mutate(RACEGR2N=case_when(
  RACE=="BLACK OR AFRICAN AMERICAN" ~ 1,
  !is.na(RACE) ~ 2,
  is.na(RACE)  ~ 3
))



```




#32

```{r}
adsl_1 <- adsl_1 %>% mutate(ETHNICN = case_when(
  ETHNIC=="HISPANIC OR LATINO"~ 1,
  ETHNIC=="NOT HISPANIC OR LATINO"~2
))



```





#33
```{r}
adsl_1 <- adsl_1 %>% mutate(AETHNIC = case_when(
  ETHNIC == NA~"Missing",
  ETHNIC=="HISPANIC OR LATINO"~"HISPANIC OR LATINO" ,
  ETHNIC=="NOT HISPANIC OR LATINO"~"NOT HISPANIC OR LATINO"
))
```

#34

```{r}
adsl_1 <- adsl_1 %>% mutate(AETHNICN =case_when(
  AETHNIC == "HISPANIC OR LATINO"~1,
  AETHNIC =="NOT HISPANIC OR LATINO"~2,
  AETHNIC == NA ~3
  
)
)

```
#36
```{r}
adsl_1 <- adsl_1 %>% mutate(COUNTRYN = case_when(
  COUNTRY == "USA"~84,
  COUNTRY == "CAN" ~14
)
)

```


#37
#problem






#41



```{r}




dummy1<- ds %>% 
  filter(DSSCAT =="SCREEN") %>%
  select(DSSCAT,DSSTDTC,VISITNUM,USUBJID)
  
pr <- dummy1 %>% mutate(SCRNFL=case_when(
  (DSSCAT == "SCREEN" & DSSTDTC !=NA) | VISITNUM == 10 ~"Y",
  TRUE ~"N"
)) %>% distinct(USUBJID,.keep_all = TRUE)%>%
   select(SCRNFL,USUBJID)
adsl_1 <- adsl_1 %>% full_join(pr)



```


#42


```{r}

adsl_1 <- adsl_1 %>% 
  mutate(SCRNFN = case_when(
    SCRNFL =="Y"~1,
    TRUE ~2
  )
)


```



#43

```{r}

dm2 <- ds %>% select(DSDECOD,DSSCAT,USUBJID)

pr2 <- dm2 %>% mutate(ENRLFL=case_when(
  DSDECOD =='INFORMED CONSENT OBTAINED' & DSSCAT =='STUDY'~"N",
  DSDECOD !='INFORMED CONSENT OBTAINED' & DSSCAT !='STUDY' ~"Y"
)) %>% distinct(USUBJID,.keep_all = TRUE) %>%
  select(USUBJID,ENRLFL)

adsl_1 <- adsl_1 %>% full_join(pr2)




```


#44

```{r}

adsl_1 <- adsl_1 %>%
  mutate(ENRLFN = case_when(
    ENRLFL =="Y"~1,
    TRUE ~2
  )
)

```



#49

IF IN DS THERE IS A RECORD WITH(DSSCAT='STUDY CONCLUSION'
AND EPOCH='FOLLOW-UP' AND DSDECOD='COMPLETED') 
OR (DSDECOD = 'CONTINUATION TO FOLLOW UP PHASE') 
THEN LTFUFL = "Y". ELSE "N".


```{r}

dm3 <- ds %>% filter(DSSCAT == 'STUDY CONCLUSION' | EPOCH =='FOLLOW-UP' |
                       DSDECOD=="COMPLETED" | DSDECOD ==
                       'CONTINUATION TO FOLLOW UP PHASE')

pr3 <- dm3 %>% mutate(LTFUFL=
case_when(
 ( DSSCAT == 'STUDY CONCLUSION' &
    EPOCH =='FOLLOW-UP' &
    DSDECOD=="COMPLETED") |
   DSDECOD == 'CONTINUATION TO FOLLOW UP PHASE' ~"Y",
 TRUE~"N"
)) %>% distinct(USUBJID,.keep_all = TRUE)%>%
  select(USUBJID,LTFUFL)



adsl_1 <- adsl_1 %>% full_join(pr3)

table(adsl$LTFUFL)
table(adsl_1$LTFUFL)
```


#50

```{r}


adsl_1 <- adsl_1 %>% mutate(LTFUFN = case_when(
  LTFUFL == "Y"~1,
  TRUE~2
)
)
```

#51
#IF SUBJECT HAS TWO CONSECUTIVE RECORDS (BUT ON DIFFERENT DAYS) WHERE #LB.LBTESTCD="HIV1RNA" AND LB.LBMETHOD="POLYMERASE CHAIN REACTION" AND LB.LBSTRESN #>= 200 THEN CVFFL="Y", ELSE CVFFL="N". NOTE: IF A SUBJECT HAS MORE THAN ONE RECORD #ON THE SAME DAY, THEN TAKE THE WORST VALUE (I.E. THE MAXIMUM VALUE).



```{r}

dm4 <- lb %>% filter(LBTESTCD == "HIV1RNA" |
                       LBMETHOD=="POLYMERASE CHAIN REACTION" |
                       LBSTRESN >=200)

pr4 <- dm4 %>% mutate(CVFFL=case_when(
  (LBTESTCD == "HIV1RNA" &
                       LBMETHOD=="POLYMERASE CHAIN REACTION" &
                       LBSTRESN >=200) ~"Y",
  TRUE ~"N"
)) %>% distinct(USUBJID,.keep_all = TRUE) %>% select(USUBJID,CVFFL)


adsl_1 <- adsl_1 %>% full_join(pr4)

```


#52



```{r}
adsl_1 <- adsl_1 %>% mutate(CVFFN= case_when(
  CVFFL=="Y"~1,
  TRUE ~ 0
)
)




```

#58


```{r}

adsl_1 <- adsl_1 %>% mutate(TRTO1PN=case_when(
  ARM =="CAB LA (600 mg) + RPV LA (900 mg) Q2M"~"1",
  ARM =="Oral DTG (50mg) + RPV (25mg) daily"~"2",
  ARM == "Not Assigned"~"3"
 ))
```


#57


```{r}
adsl_1 <- adsl_1 %>% mutate(TRT01P = case_when(
  TRTO1PN =="1"~ "Q2M",
  TRTO1PN =="2"~"DTG+RPV",
  TRTO1PN =="3"~"Not Assigned"
)
)
```











# 60

```{r}
adsl_1 <- adsl_1 %>% mutate(TRT01AN = case_when(
  ACTARM =="CAB LA (600 mg) + RPV LA (900 mg) Q2M" ~"1",
  ACTARM =="Oral DTG (50mg) + RPV (25mg) daily" ~"2",
  ACTARM =="Not Assigned"~"3"
)
)





```



#59


```{r}
adsl_1 <- adsl_1 %>% mutate(TRT01A=case_when(
  TRT01AN =="1"~"Q2M",
  TRT01AN =="2" ~ "DTG + RPV",
  TRT01AN =="3"~"Not Assigned"
  
  
)
)


```



#39

IF TRT01A IS NOT MISSING AND SUBJECT HAS A RECORD WHERE EX.EXSTDTC IS NOT MISSING THEN SAFFL="Y", ELSE SAFFL="N".


```{r}

dm5 <- ex %>% 
  filter(!is.na(EXSTDTC) == TRUE) %>% 
  distinct(USUBJID,.keep_all = TRUE) %>%
  select(USUBJID,EXSTDTC)

adsl_1 <- adsl_1 %>%
  full_join(dm5) %>%
  mutate(SAFFL=case_when(
    !is.na(TRT01A) & !is.na(EXSTDTC)~"Y",
    TRUE ~"N"
  ))

```



#40


```{r}

adsl_1 <- adsl_1 %>% mutate(SAFFN = case_when(
  SAFFL =="Y"~1,
  TRUE~0
)
)



```




#41


IF (UPCASE(DS.DSSCAT)="SCREEN" AND DS.DSSTDTC IS NOT NULL) OR (INT(VISITNUM)=10 AND SV.SVSTDTC IS NOT NULL) THEN SCRNFL="Y", ELSE SCRNFL="N".


```{r}

try1<- ds %>% filter(DSSCAT=="SCREEN") %>% 
  distinct(USUBJID,.keep_all = TRUE) %>%
  select(DSSCAT,DSSTDTC,VISITNUM,USUBJID)
try2 <- sv %>% filter(!is.na(SVSTDTC)==TRUE) %>% 
  distinct(USUBJID,.keep_all = TRUE) %>%
  select(USUBJID,SVSTDTC)

try3<- try1 %>% mutate(SCRNFL=case_when(
  (DSSCAT =="SCREEN" &
    !is.na(DSSTDTC) ) |
   ( VISITNUM =10 &
    !is.na(try2$SVSTDTC)) ~"Y",
  TRUE ~"N"
)) %>% 
  select(USUBJID,SCRNFL)


adsl_1 <- adsl_1 %>% full_join(try3)

rm(try1,try2,try3)
  

```



#42


```{r}
adsl_1 <- adsl_1 %>%
  mutate(SCRNFN =case_when(
    SCRNFL == "Y" ~ 1,
    TRUE~2
  )
)


```




#43

ENRLFL ASSIGNED VALUE OF "N" UNLESS A SUBJECT HAS A DISPOSITION RECORD WHERE THE VALUE OF DSDECOD SHOWS 'INFORMED CONSENT OBTAINED' AND THE VALUE OF DSSCAT SHOWS 'STUDY'  THEN ENRLFL IS ASSIGNED "Y".


```{r}

try1 <- ds %>% mutate(ENRLFL=case_when(
  !is.na(DSCAT) &
    DSDECOD =='INFORMED CONSENT OBTAINED' &
    DSSCAT =="STUDY" ~"N",
  TRUE~"Y"
)) %>% distinct(USUBJID,.keep_all = TRUE) %>%
  select(USUBJID,ENRLFL)
adsl_1 <- adsl_1 %>% full_join(try1)
rm(try1)

```



#44


```{r}

adsl_1 <- adsl_1 %>% mutate(ENRLFN=case_when(
  ENRLFL =="Y"~1,
  TRUE~2
)
)


```





#61
Numeric date part of the earliest EX.EXSTDTC. where EXTRT contains CAB LA or RPV LA or DOLUTEGRAVIR



```{r}
try1<- ex %>% 
  filter(EXTRT =="CAB LA" | EXTRT =="RPV LA" |
           EXTRT == "DOLUTEGRAVIR/RILPIVIRINE" ) %>%
  group_by(USUBJID) %>%
  mutate(TRTSDT=as.Date(min(EXSTDTC))) %>%
  summarise_all(first) %>%
  select(USUBJID,TRTSDT)

adsl_1 <- adsl_1 %>% full_join(try1)
rm(try1)
table(adsl_1$TRTSDT)

```

#62
Numeric date part of the latest of EX.EXSTDTC and EX.EXENDTC. where EXTRT contains CAB LA or RPV LA or DOLUTEGRAVIR



```{r}

try1<- ex %>% 
  filter(EXTRT =="CAB LA" | EXTRT =="RPV LA" |
           EXTRT == "DOLUTEGRAVIR/RILPIVIRINE" ) %>%
  group_by(USUBJID) %>%
  mutate(TRTEDT=as.Date(max(EXSTDTC))) %>%
  summarise_all(last) %>%
  select(USUBJID,TRTEDT)

adsl_1 <- adsl_1 %>% full_join(try1)

sum(is.na(adsl_1$TRTEDT))

rm(try1)

```


#46

IF TRT01P IS NOT MISSING AND SUBJECT HAS A RECORD WHERE EX.EXSTDTC IS NOT MISSING THEN ITTEFL="Y", ELSE ITTEFL="N".

```{r}

try14 <- ex 

try15 <- adsl_1
 try15 <- full_join(try15,try14) %>%
   distinct(USUBJID,.keep_all = T)
 try15 <- try15 %>% mutate(ITTEFL=case_when(
   !is.na(TRT01P) &
     !is.na(SUBJID) &
     !is.na(EXSTDTC) ~"Y",
   TRUE~"N"
 )) %>% select(USUBJID,ITTEFL)
 
 adsl_1 <- adsl_1 %>% full_join(try15)
 


```

#47
EQUIVALENT OF ITTEFL

```{r}

adsl_1 <- adsl_1 %>% mutate(MNTFL=ITTEFL
)

```


#63

IF SUBJECT WITH MNTFL VALUE OF "Y" ALSO HAS A RECORD WHERE DS.DSSCAT="STUDY CONCLUSION" THEN MNTCMPS="COMPLETED", ELSE IF MNTFL="Y" AND DS.DSSCAT="STUDY TREATMENT DISCONTINUATION" THEN MNTCMPS="WITHDRAWN", ELSE IF MNTFL="Y" THEN  MNTCMPS="ONGOING".

```{r}

try1 <- ds %>% filter(DSSCAT =="STUDY CONCLUSION" |
                        DSSCAT=="STUDY TREATMENT DISCONTINUATION") %>%
  select(USUBJID,DSSCAT)
try2 <- adsl_1
try2 <- try2 %>% full_join(try1)

try2 <-  try2 %>% mutate(MNTCMPS=case_when(
  MNTFL == "Y" &
    DSSCAT =="STUDY CONCLUSION" ~"COMPLETED",
  MNTFL =="Y" &
    DSSCAT =="STUDY TREATMENT DISCONTINUATION" ~ "WITHDRAWN",
  MNTFL=="Y"~"ONGOING"
)
                         ) %>% select(USUBJID,MNTCMPS) %>% distinct(USUBJID,.keep_all = TRUE)


adsl_1 <- adsl_1 %>% distinct(USUBJID,.keep_all = TRUE) %>%
  full_join(try2) %>% distinct(USUBJID,.keep_all = TRUE)


rm(try1,try2)
```



#64


```{r}
adsl_1 <- adsl_1 %>% mutate(MNTCMPSN= case_when(
  MNTCMPS == "COMPLETED" ~1,
  MNTCMPS == "WITHDRAWN"~2,
  MNTCMPS =="ONGOING" ~3,
  TRUE ~4
))
```



#66


IF SUBJECT HAS A RECORD WHERE DSSCAT='STUDY CONCLUSION' AND EPOCH='FOLLOW-UP' AND DSDECOD='COMPLETED' AND TRT01P NE 'DTG + RPV' THEN LTFCMPS='COMPLETED'. ELSE IF DSDECOD='CONTINUATION TO FOLLOW UP PHASE' AND TRT01P NE 'DTG + RPV' THEN LTFCMPS='ONGOING'.


```{r}

try1 <- ds %>% filter(DSSCAT =="STUDY CONCLUSION" | 
                        EPOCH=='FOLLOW-UP' |
                        DSDECOD=='COMPLETED' |
                        DSDECOD =='CONTINUATION TO FOLLOW UP PHASE') %>%
  select(USUBJID,DSSCAT,EPOCH,DSDECOD) %>%
  distinct(USUBJID,.keep_all = TRUE)

try2 <- adsl_1 

try2 <- try2 %>% full_join(try1)  %>%
  mutate(LTFCMPS=case_when(
    DSSCAT =="STUDY CONCLUSION" &
     EPOCH=='FOLLOW-UP' &
      DSDECOD =='COMPLETED'  &
      TRT01P != 'DTG + RPV' ~"COMPLETED",
    DSDECOD =='CONTINUATION TO FOLLOW UP PHASE' &
      TRT01P !='DTG + RPV'~"ONGOING",
    TRUE~"NA"
  )) %>%
  select(USUBJID,LTFCMPS)


adsl_1 <- adsl_1 %>%
  full_join(try2) %>% distinct(USUBJID,.keep_all = TRUE)
rm(try1,try2)

```






#67
IF THE VALUE OF LTFCMPS SHOWS "ONGOING" THEN LTFCMPSN =1; IF IT SHOWS "COMPLETED" THEN LTFCMPSN =2; IF IT SHOWS "WITHDRAWAL" THEN LTFCMPSN =3;

```{r}

adsl_1<- adsl_1 %>% mutate(LTFCMPSN=case_when(
  LTFCMPS =="ONGOING"~1,
  LTFCMPS =="COMPLETED"~2,
  LTFCMPS =="WITHDRAWAL"~3
  
))
```




#68

IF SUBJECT HAS A RECORD WHERE CE.CECAT="LIVER EVENT REPORTING" AND (SUPPCE.QNAM="LERMX" AND SUPPCE.QVAL="LIVER EVENT STOPPING CRITERIA") THEN LSEFL="Y", ELSE LSEFL="N".



```{r}
try1 <- ce %>% mutate(LSEFL=case_when(
  ce$CECAT =="LIVER EVENT REPORTING"&
    suppce$QNAM=="LERMX" &
    suppce$QVAL =="LIVER EVENT STOPPING CRITERIA" ~"Y",
  TRUE ~"N"
)) %>% select(LSEFL,USUBJID)

adsl_1 <- adsl_1 %>% full_join(try1)
rm(try1)

```






#69
```{r}


adsl_1 <- adsl_1 %>% mutate(LSEFN=case_when(
  LSEFL =="Y"~1,
  TRUE~2
)
)




```



#71

IF DTHFL="Y" THEN DTHFN=1, BLANK OTHERWISE.
```{r}
adsl_1 <- adsl_1 %>% mutate(DTHFN=case_when(
  DTHFL == "Y"~"1",
  TRUE~ ""
))


```



#72

WHEN COUNTRY='CAN' THEN ASSIGN ACOUNTRY='CANADA'; ELSE WHEN COUNTRY='USA' ASSIGN ACOUNTRY='UNITED STATES'



```{r}
adsl_1 <- adsl_1 %>% mutate(ACOUNTRY = case_when(
  COUNTRY =="CAN"~"CANADA",
  COUNTRY =="USA"~"UNITED STATES"
))


```




#73


IF SUBJECT HAS A RECORD WHERE THE VALUE OF VISIT CONTAINS 'END OF MAINTENANCE PHASE' OR (DS.DSSCAT CONTAINS 'DISCONTINU' AND  'STUDY'). AND TRTSDT FOR THIS PERSON IS NOT MISSING, THEN MDSFL="Y". OTHERWISE MDSFL IS "N".



```{r}
try1<- ds %>% filter(VISIT == 'END OF MAINTENANCE PHASE' |
                       DSSCAT=='STUDY TREATMENT DISCONTINUATION') %>%
  distinct(USUBJID,.keep_all = TRUE)

try2 <- adsl_1
try2 <- try2  %>%full_join(try1) %>% mutate(MDSFL=case_when(
  VISIT == 'END OF MAINTENANCE PHASE'  |
    (DSSCAT=='STUDY TREATMENT DISCONTINUATION' &
    !is.na(TRTSDT)) ~"Y",
  TRUE~"N"
    
)) %>% select(USUBJID,MDSFL)

adsl_1 <- adsl_1 %>% full_join(try2)


rm(try1,try2)

```



#74

Only populate for subjects with MDSFL = "Y". Find records in DS where visit contains 'END OF MAINTENANCE PHASE' or (DSSCAT contains "DISCONTINU" and  'STUDY'). DISCREAS then equals DS.DSDECOD.

```{r}
try1<- ds %>% filter(VISIT == 'END OF MAINTENANCE PHASE' |
                       DSSCAT=='STUDY TREATMENT DISCONTINUATION') %>%
  distinct(USUBJID,.keep_all = TRUE)
try2 <- adsl_1 


try2 <- try2 %>% full_join(try1) 
try2 <- try2 %>% mutate(DISCREAS=case_when(
  MDSFL == "Y" &
    VISIT == "END OF MAINTENANCE PHASE" |
    DSSCAT == "STUDY TREATMENT DISCONTINUATION" ~ as.character(DSDECOD),
  T ~"na"
)) %>% select(USUBJID,DISCREAS)

adsl_1 <- adsl_1 %>% full_join(try2) %>% distinct(USUBJID,.keep_all = TRUE)
rm(try1,try2)
```





#75


MNTSDT IS EQUIVALENT TO TRTSDT.



```{r}


adsl_1<- adsl_1 %>% mutate(MNTSDT=TRTSDT)

```



#76

If the subject is rescreened (i.e. DM.SUBJID="MULTPLE") then concatenate all of the subject's screening dates from DS.DSSTDTC (converted to DATE9. format) where DS.VISITNUM = 10 together, separated by a comma.








#80
```{r}
try1<- vs %>% filter(VSDY <=1) %>%
  filter(VSTEST == "Height" | VSTEST ==  "Weight") %>%
  select(USUBJID,VSTEST,VSORRES) %>% 
  pivot_wider(names_from = VSTEST,values_from = VSORRES)


try1$Height <- as.numeric(try1$Height)
try1$Weight <- as.numeric(try1$Weight)

try1 <- try1 %>% mutate(BMIBL = Weight/((Height/100)*(Height/100))) %>%
  select(BMIBL,USUBJID)

adsl_1 <- adsl_1 %>% full_join(try1)

rm(try1)




```


#81
#IF . < BMIBL < 30 THEN BMIGR1N=1, ELSE IF BMIBL >= 30 THEN BMIGR1N=2, 
#OTHERWISE BLANK.

```{r}
adsl_1 <- adsl_1 %>% mutate(BMIGR1N=case_when(
  BMIBL <30~1,
  BMIBL >=30 ~2
))


adsl_1 <- adsl_1 %>% distinct(USUBJID,.keep_all = TRUE)


```
#82

```{r}
adsl_1 <- adsl_1 %>% mutate(BMIGR1=case_when(
  BMIGR1N==1~"<30",
  BMIGR1N == 2~ ">=30"
  
))

```
#83




#BMIUNIT = 'kg/m2' if bmibl=weightbl/((heightbl/100)*(heightbl/100)) is not Null.
```{r}
adsl_1 <- adsl_1 %>% mutate(BMIUNIT=case_when(
  is.na(BMIGR1N)~"na",
  TRUE ~"kg/m2"
))

```

#84
#HTUNIT = VSSTRESU where VSTESTCD="HEIGHT" and ^missing(VSSTRESN)

```{r}

try1<- vs %>% filter(VSTESTCD =="HEIGHT") %>% select(USUBJID,VSTESTCD,VSSTRESN,VSSTRESU,VSDTC)
 
try2<- adsl_1 
 try2 <- try2 %>% full_join(try1)%>%
mutate(HTUNIT=case_when(
  VSTESTCD =="HEIGHT" & !is.na(VSSTRESN)~ as.character(VSSTRESU),
  TRUE~"na"
)) %>% select(USUBJID,HTUNIT)

adsl_1 <- adsl_1 %>% full_join(try2) %>% distinct(USUBJID,.keep_all = T)


rm(try1,try2)

```
#85

#SELECT LATEST RECORDS WHERE UPCASE(VSTESTCD) CONTAINS 'HEIGHT'
# AND NON-NULL VSDTC VALUES ARE EITHER  BEFORE OR ON THE TREATMENT START DATE.  
#  HEIGHTBL=VSSTRESN
```{r}
try1<- vs %>% filter(VSTESTCD =="HEIGHT") %>% select(USUBJID,VSTESTCD,VSSTRESN,VSSTRESU,VSDTC)


try2 <- adsl_1
try2<- try2 %>% full_join(try1) %>% mutate(HEIGHTBL=case_when(
  VSTESTCD =="HEIGHT" & !is.na(VSDTC)~as.character(VSSTRESN),
  TRUE~"na"
)) %>% select(USUBJID,HEIGHTBL)

adsl_1 <- adsl_1 %>% full_join(try2)


rm(try1,try2)

```
#86
#WTUNIT = VSSTRESU where VSTESTCD="WEIGHT" and ^missing(VSSTRESN)
```{r}
dum1<- vs %>% filter(VSTESTCD == "WEIGHT") %>% select(USUBJID,VSSTRESU,VSTESTCD,VSSTRESN,VSDTC)
dum1 <- dum1 %>% distinct(USUBJID,.keep_all = TRUE)
try2<- adsl_1

try2 <- full_join(try2,dum1)
try2 <- try2 %>% mutate(WTUNIT=case_when(
  VSTESTCD =="WEIGHT" & !is.na(VSSTRESN)~as.character(VSSTRESU),
  TRUE~"na"
)) %>% select(USUBJID,WTUNIT)


adsl_1 <- adsl_1 %>% full_join(try2)


rm(try2)
  
```


#87
#SELECT LATEST RECORDS WHERE UPCASE(VSTESTCD) CONTAINS 'WEIGHT' 
#AND NON-NULL VSDTC VALUES ARE EITHER  BEFORE OR ON THE TREATMENT START DATE.    
#WEIGHTBL=VSSTRESN

```{r}
dum1<- vs %>% filter(VSTESTCD == "WEIGHT") %>% select(USUBJID,VSSTRESU,VSTESTCD,VSSTRESN,VSDTC)

try2 <- adsl_1
try2<- try2 %>% full_join(dum1) %>% mutate(WEIGHTBL=case_when(
  VSTESTCD =="WEIGHT" & !is.na(VSDTC)~as.character(VSSTRESN),
  TRUE~"na"
)) %>% select(USUBJID,WEIGHTBL)

adsl_1 <- adsl_1 %>% full_join(try2)

rm(try2)
```




#88
#If subject has a pre-treatment record where CO.COVAL="HBV DNA DETECTED" 
#then HEPBST="Positive". 
#Else if subject has a pre-treatment record where LB.LBTESTCD in 
#("HBVDNA" "HBVDNAC" "HBVDNAL"): if LB.LBSTRESN ne . or LB.LBORRES ne "<x" 
#then HEPBST="Positive", else HEPBST="Negative". 
#Else if subject has a pre-treatment record where LB.LBTESTCD="HBSAGZ": 
#if LB.LBSTRESC="REACTIVE" then HEPBST="Positive", 
#else if LB.LBSTRESC="NON-REACTIVE" then HEPBST="Negative".

```{r}

try1<- co %>% filter(COVAL=="HBV DNA DETECTED" )
try2 <- lb  %>% filter(EPOCH=="FOLLOW-UP", LBTESTCD =="HBVDNA" &
                         LBTESTCD =="HBVDNAC"&
                         LBTESTCD =="HBVDNAL" &
                         LBTESTCD == "HBSAGZ")

try2 <- try2 %>% full_join(try1) %>%
  mutate(HEPBST=case_when(
    COVAL == "HBV DNA DETECTED" ~"Positive",
    (LBTESTCD =="HBVDNA" &
      LBTESTCD =="HBVDNAC" & LBTESTCD =="HBVDNAL") ~"Positive",
      
    TRUE~"Negative"
  )) %>% select(USUBJID,HEPBST)

adsl_1 <- adsl_1 %>% full_join(try2)%>%
  distinct(USUBJID,.keep_all = T)
table(adsl_1$HEPBST)
table(adsl$HEPBST)

```
#94
#Numeric date part of the latest of EX.EXSTDT and EX.EXENDT 
#where EX.EXROUTE="ORAL" or EX.EXTPT="ORAL DOSE".
# Set to TRTEDT for TRT01PN=2.
```{r}




```








#97
#VALUE OF SVSTDTC WHERE VISIT='MONTH 12'

```{r}
a2<- sv %>% filter(VISIT == "MONTH 12") %>% select(USUBJID,SVSTDTC,VISIT)

adsl_1<- full_join(adsl_1,a2)



adsl_1 <- adsl_1 %>% mutate(MTH12SDT=case_when(
  VISIT =="MONTH 12" ~ as.character(SVSTDTC),
  TRUE ~"NA"
)
) %>% select(-SVSTDTC,-VISIT)

```
#VALUE OF SVSTDTC WHERE VISIT='MONTH 26'
#MTH26SDT

#98
```{r}
a3<- sv %>% filter(VISIT == "MONTH 26") %>% select(USUBJID,SVSTDTC,VISIT)

adsl_1<- full_join(adsl_1,a3)



adsl_1 <- adsl_1 %>% mutate(MTH26SDT=case_when(
  VISIT =="MONTH 26" ~ as.character(SVSTDTC),
  TRUE ~"NA"
)
) %>% select(-SVSTDTC,-VISIT)



```

#99
#IF SUBJECT HAS A RECORD WHERE Y8.Y8TESTCD="HIVRFKNW" THEN HIVRKFL="Y",
# ELSE HIVRKFL="N".
```{r}
y8 <- read_sas("sdtm/y8.sas7bdat", NULL)

a12<- y8 %>% filter(Y8TESTCD=="HIVRFKNW") %>% select(USUBJID,Y8TESTCD)
adsl_1 <- full_join(adsl_1,a12)
adsl_1 <- adsl_1 %>% mutate(HIVRKFL = case_when(
  Y8TESTCD == "HIVRFKNW" ~"Y",
  TRUE~"N"
))

```










#90
If subject has a pre-treatment record where LB.LBTESTCD in ("HCVRNA" "HCVRNAL"): if LB.LBORRES ne "TARGET NOT DETECTED" or LB.LBSTRESN ne . then HEPCST="Positive", else HEPCST="Negative". Else if subject has a pre-treatment record where LB.LBTESTCD="HCVABZ": if LB.LBSTRESC in ("REACTIVE" "BORDERLINE") then HEPCST="Positive", else if LB.LBSTRESC="NON-REACTIVE" then HEPCST="Negative".




```{r}

try11<- lb %>% mutate(HEPCST=case_when(
  
  (LBTESTCD =="HCVRNA" &
     LBTESTCD=="HCVRNAL" )&
   (LBORRES !="TARGET NOT DETECTED" |
       LBSTRESN != ".") ~"Positive",
  
  
  lb$LBTESTCD == "HCVABZ" & lb$LBSTRESC == "REACTIVE" &
    lb$LBSTRESC == "BORDERLINE" ~"Positive",
  lb$LBSTRESC=="NON-REACTIVE"~"Negative"
  
))  %>% distinct(USUBJID,.keep_all = TRUE)

table(try11$HEPCST)

```


# 95
Numeric date part of the latest of EX.EXSTDTC and EX.EXENDTC where EX.EXROUTE="INTRAMUSCULAR".


Numeric date part of the earliest EX.EXSTDTC. where EXTRT contains CAB LA or RPV LA or DOLUTEGRAVIR

```{r}




```




#100


Concatenate all values of Y8.Y8STRESC where Y8.Y8TESTCD="HIVRF", separated by a semi colon. Order the values based on Y8.Y8SEQ, except for where Y8.Y8STRESC="OTHER", which should be kept last in the list of values.




```{r}
y8 <- read_sas("sdtm/y8.sas7bdat", NULL)


```




#101
The latest value of LB.LBSTRESN where LB.LBTESTCD="CD4" and LB.LBDTC is on or before TRTSDT. Note that pre-dose unscheduled visits are included.


```{r}

try1<- adsl_1 %>% full_join(lb)


try1$LBDTC <- as.Date(try1$LBDTC)

try1<- try1  %>%filter(LBTESTCD=="CD4") %>% group_by(USUBJID)%>%
  mutate(CD4BL=case_when(
    LBDTC <= TRTSDT~ LBSTRESN
  )) %>% select(USUBJID,CD4BL) %>% distinct(USUBJID,.keep_all = TRUE) 


adsl_1 <- adsl_1 %>% full_join(try1)

rm(try1)

```




#103
IF . < CD4BL < 350 THEN CD4BLG1N=1, ELSE IF 350 =< CD4BL < 500 THEN CD4BLG1N=2, ELSE IF CD4BL >= 500 THEN CD4BLG1N=3.


```{r}

adsl_1 <- adsl_1 %>% mutate(CD4BLG1N=case_when(
  CD4BL < 350~"1",
  CD4BL >=350 & CD4BL <500~"2",
  TRUE~"3",
  is.na(CD4BL)~"0"
))
```


#102


```{r}
adsl_1 <- adsl_1 %>% mutate(CD4BLGR1=case_when(
  CD4BLG1N == "1"~"<350",
  CD4BLG1N== "2"~"350-<500",
  CD4BLG1N== "3"~">=500"
)
)


```
#105




If subject has a record where CE.CECAT="HIV ASSOCIATED CONDITIONS" and CE.CESTDTC non-missing and CE.CESTDTC is on/before TRTSDT then CDCBCATN=3. Else if . < CD4BL < 200 then CDCBCATN=3, else if 200 =< CD4BL < 500 then CDCBCATN=2, else if CD4BL >= 500 then CDCBCATN=1. Else if CD4BL is missing then find the subjects latest record where LB.LBTESTCD="CD4LY" and LB.LBDTC is on/before TRTSDT, and if . < LB.LBSTRESN < 14 then CDCBCATN =3, else if 14 =< LB.LBSTRESN < 26 then CDCBCATN =2, else if LB.LBSTRESN >= 26 then CDCBCATN=1. Otherwise CDCBCATN is missing. Where CD4BL is the latest value of LB.LBSTRESN where LB.LBTESTCD="CD4" and numeric date part of LB.LBDTC is on or before TRTSDT.
```{r}

rm1<- full_join(ce,lb)
rm1$LBDTC <- as.Date(rm1$LBDTC)
rm1$CESTDTC <-as.Date(rm1$CESTDTC)

rm1<-full_join(rm1,adsl_1)
rm1<- rm1 %>% mutate(CDCBCATN=case_when(
  CECAT =="HIV ASSOCIATED CONDITIONS" &
    !is.na(CESTDTC) &
    (CESTDTC) <= TRTSDT ~"3",
  CD4BL >= 200 & CD4BL < 500 ~"2",
  CD4BL >= 500 ~"1",
  is.na(CD4BL) &
    LBTESTCD =="CD4LY" &
    (LBDTC) <=TRTSDT &
    LBSTRESN <14~"3",
  LBSTRESN >=14 & LBSTRESN <26~"2",
  LBSTRESN >=26~"1",
  TRUE ~"missing"
)
) %>% distinct(USUBJID,.keep_all = TRUE) %>% select(CDCBCATN,USUBJID)

adsl_1 <-adsl_1 %>% full_join(rm1)
rm(rm1)
```



#106
If subject has a record where MH.MHTERM="DEPRESSION" and MH.MHOCCUR="Y" and MH.VISITNUM=10 and MH.MHSTRF="BEFORE" then HISDEPFL="Y", else HISDEPFL="N".


```{r}

mh <- read_sas("sdtm/mh.sas7bdat", NULL)

rm(rm1)
rm2<-mh %>% filter(
                     MHTERM =="DEPRESSION"&
                     MHOCCUR=="Y" &
                     VISITNUM ==10 &
                   MHSTRF =="BEFORE"
                   )
rm1<- rm2 %>% 
  mutate(HISDEPFL=case_when(
  MHPRESP =="Y" & 
    MHTERM == "DEPRESSION" &
    MHOCCUR =="Y" &
    VISITNUM ==10 &
    MHSTRF =="BEFORE" ~"Y",
TRUE~"N"  
)) %>% select(HISDEPFL,USUBJID) #%>% distinct(USUBJID,.keep_all = TRUE)


adsl_1 <- adsl_1 %>% full_join(rm1) %>% distinct(USUBJID,.keep_all = TRUE)
adsl_1$HISDEPFL[is.na(adsl_1$HISDEPFL)]<-"N"
table(adsl_1$HISDEPFL)

```



#107
If subject has a record where MH.MHTERM="SUICIDAL IDEATION" and MH.MHOCCUR="Y" and MH.MHOCCUR="Y" and MH.MHSTRF="BEFORE" then HISDEPFL="Y", else HISDEPFL="N".





```{r}

rm1<- mh %>% filter(MHTERM=="SUICIDAL IDEATION" &
                     MHOCCUR=="Y" &
                      MHOCCUR=="Y" &
                     MHSTRF=="BEFORE" )

rm1 <- rm1 %>% mutate(HISSUIFL=case_when(
  MHTERM=="SUICIDAL IDEATION" &
                     MHOCCUR=="Y" &
                      MHOCCUR=="Y" &
                     MHSTRF=="BEFORE" ~"Y",
  TRUE ~ "N"
)) %>% select(HISSUIFL,USUBJID)

adsl_1 <- adsl_1 %>% full_join(rm1)


adsl_1$HISSUIFL[is.na(adsl_1$HISSUIFL)]<-"N"

rm(rm1)

```

#108



If subject has a record where MH.MHTERM="ANXIETY" and MH.MHOCCUR="Y" and MH.VISITNUM=10 and MH.MHSTRF="BEFORE" then HISDEPFL="Y", else HISDEPFL="N".

```{r}

try1 <- mh %>% filter(MHTERM == "ANXIETY" &
                        MHOCCUR=="Y" &
                        VISITNUM==10 &
                        MHSTRF=="BEFORE")

try1 <- try1 %>% mutate(HISANXFL= case_when(
  MHTERM == "ANXIETY" &
                        MHOCCUR=="Y" &
                        VISITNUM==10 &
                        MHSTRF=="BEFORE" ~"Y",
  TRUE~"N"
)) %>% select(HISANXFL,USUBJID)
adsl_1 <- adsl_1 %>% full_join(try1)
adsl_1$HISANXFL[is.na(adsl_1$HISANXFL)]<- "N"
rm(try1)
```


#109

If HISANXFL="Y" then HISANX="previous history of anxiety", else HISANX="no previous history of anxiety".


```{r}

adsl_1 <- adsl_1 %>% mutate(HISANX= case_when(
  HISANXFL =="Y"~"previous history of anxiety",
  TRUE~"no previous history of anxiety"
))


```




#110

If HISSUIFL="Y" then HISSUI="previous history of suicidal ideation", else HISSUI="no previous history of suicidal ideation".




```{r}

adsl_1 <- adsl_1 %>% mutate(HISSUI=case_when(
  HISSUIFL =="Y"~ "previous history of suicidal ideation",
  TRUE~"no history of suicidal ideation"
))


```

#111


If HISDEPFL="Y" then HISDEP="previous history of depression", else HISDEP="no previous history of depression".


```{r}
adsl_1 <- adsl_1 %>% mutate(HISDEP=case_when(
  HISDEPFL =="Y"~"previous history of depression",
  TRUE~"no previous history of depression"
))


```



#88

